---
title: "LimnoPalettes"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(
  fig.path = "man/figures/"
)
```

## Table of Contents

* [Citing package](#cite)
* [Installation](#install)
* [Palettes](#examp)
* [Working Examples](#workexamp)

Code and general idea inspired by the ["Wes Anderson Palettes"](https://github.com/karthik/wesanderson) R-Package.

## Citing package <a name="cite"></a>

```{r}
citation('LimnoPalettes')
```

## Installation <a name="install"></a>

```{r,eval=F}
install.packages("devtools");# if you do not have it installed on your PC
devtools::install_github("SwampThingPaul/LimnoPalettes")
```


## Now Presenting... <a name="examp"></a>

```{r iowa,fig.height=5,fig.width=7,align='center',echo=FALSE,message=FALSE,warning=FALSE}
library(imager)
library(LimnoPalettes)

im=load.image("./images/SummerIowaLakes_GWilkinson.jpg")

par(family="serif",mar=c(0,0,0,0))
layout(matrix(1:3,3,1),heights=c(1,1,0.25))
plot(im,ann=F,axes=F)
print(limno_palette("IowaSummer"),cex=2)
plot(0:1,0:1,ann=F,axes=F,type="n")
text(0,0.5,"Photo Credit: Grace Wilkinson (Twitter: goodgracious23)",adj=0)
```

```{r PeriFA,fig.height=5,fig.width=7,align='center',echo=FALSE,message=FALSE,warning=FALSE}
im=load.image("./images/PeriphytonFA_MMeyer.jpg")

par(family="serif",mar=c(0,0,0,0))
layout(matrix(1:3,3,1),heights=c(1,1,0.25))
plot(im,ann=F,axes=F)
print(limno_palette("PeriFA"),cex=2)
plot(0:1,0:1,ann=F,axes=F,type="n")
text(0,0.5,"Photo Credit: Michael Meyer (Twitter: mishafredmeyer)",adj=0)
```

```{r Bloom1,fig.height=5,fig.width=7,align='center',echo=FALSE,message=FALSE,warning=FALSE}
im=load.image("./images/Bloom1_SBurnet.jpg")

par(family="serif",mar=c(0,0,0,0))
layout(matrix(1:3,3,1),heights=c(1,1,0.25))
plot(im,ann=F,axes=F)
print(limno_palette("Bloom1"),cex=2)
plot(0:1,0:1,ann=F,axes=F,type="n")
text(0,0.5,"Photo Credit: Sarah Burnet (Twitter: limnosarah)",adj=0)
```

```{r Bloom2,fig.height=5,fig.width=7,align='center',echo=FALSE,message=FALSE,warning=FALSE}
im=load.image("./images/Bloom2_SBurnet.jpg")

par(family="serif",mar=c(0,0,0,0))
layout(matrix(1:3,3,1),heights=c(1,1,0.25))
plot(im,ann=F,axes=F)
print(limno_palette("Bloom2"),cex=2)
plot(0:1,0:1,ann=F,axes=F,type="n")
text(0,0.5,"Photo Credit: Sarah Burnet (Twitter: limnosarah)",adj=0)
```

```{r SuperIce,fig.height=5,fig.width=7,align='center',echo=FALSE,message=FALSE,warning=FALSE}
im=load.image("./images/LakeSuperiorIce_SBurnet.jpg")

par(family="serif",mar=c(0,0,0,0))
layout(matrix(1:3,3,1),heights=c(1,1,0.25))
plot(im,ann=F,axes=F)
print(limno_palette("SuperIce"),cex=2)
plot(0:1,0:1,ann=F,axes=F,type="n")
text(0,0.5,"Photo Credit: Sarah Burnet (Twitter: limnosarah)",adj=0)
```

```{r FlatheadRocks,fig.height=5,fig.width=7,align='center',echo=FALSE,message=FALSE,warning=FALSE}
im=load.image("./images/FlatheadLake_PJulian.jpg")

par(family="serif",mar=c(0,0,0,0))
layout(matrix(1:3,3,1),heights=c(1,1,0.25))
plot(im,ann=F,axes=F)
print(limno_palette("FlatheadRocks"),cex=2)
plot(0:1,0:1,ann=F,axes=F,type="n")
text(0,0.5,"Photo Credit: Paul Julian (Twitter: SwampThingPaul)",adj=0)
```

```{r ShelburnePond,fig.height=5,fig.width=7,align='center',echo=FALSE,message=FALSE,warning=FALSE}
im=load.image("./images/ShelburnePond_LBorre.jpg")

par(family="serif",mar=c(0,0,0,0))
layout(matrix(1:3,3,1),heights=c(1,1,0.25))
plot(im,ann=F,axes=F)
print(limno_palette("ShelburnePond"),cex=2)
plot(0:1,0:1,ann=F,axes=F,type="n")
text(0,0.5,"Photo Credit: Lisa Borre (Twitter: lisa_borre)",adj=0)
```

```{r WetSoil,fig.height=5,fig.width=7,align='center',echo=FALSE,message=FALSE,warning=FALSE}
im=load.image("./images/wetsoil_RKBhomia.jpg")

par(family="serif",mar=c(0,0,0,0))
layout(matrix(1:3,3,1),heights=c(1,1,0.25))
plot(im,ann=F,axes=F)
print(limno_palette("WetSoil"),cex=2)
plot(0:1,0:1,ann=F,axes=F,type="n")
text(0,0.5,"Photo Credit: Rupesh K Bhomia (Twitter: RupeshKBhomia)",adj=0)
```

```{r OrdRiver,fig.height=5,fig.width=7,align='center',echo=FALSE,message=FALSE,warning=FALSE}
im=load.image("./images/OrdRiverWA_CFowler.jpg")

par(family="serif",mar=c(0,0,0,0))
layout(matrix(1:3,3,1),heights=c(1,1,0.25))
plot(im,ann=F,axes=F)
print(limno_palette("OrdRiver"),cex=2)
plot(0:1,0:1,ann=F,axes=F,type="n")
text(0,0.5,"Photo Credit: Courtney Fowler (Twitter: courtzfowler)",adj=0)
```

***

## Working Examples. <a name="workexamp"></a>

```{r examp1,fig.height=4,fig.width=6,echo=TRUE,include=TRUE}
set.seed(1)
dat = data.frame(Group=c(rep("A",10),rep("B",10),rep("C",10),rep("D",10)),
                  var1=rnorm(40),var2=runif(40,1,15),var3=rpois(40,3))

cols = limno_palette("SuperIce",4)
boxplot(var2~Group,dat, col=cols)
```
```{r examp2,fig.height=4,fig.width=6}
cols = limno_palette("IowaSummer",4,"continuous")
cols2 = cols[dat$Group]
plot(var2~var3,dat,pch=21,bg=cols2,cex=2)
```

```{r examp3,fig.height=4,fig.width=6,echo=TRUE,include=TRUE}
cols = limno_palette("PeriFA",4,"continuous")
barplot(aggregate(dat$var3,list(dat$Group),mean)$x,names.arg=unique(dat$Group),ylim=c(0,4),col=cols)

```

While not a part of this package, for data visualization purposes it would be a good idea to see how these colors are perceived for people with color blindness. 

```{r,fig.width=9,fig.height=7,warning=FALSE,echo=TRUE,include=TRUE}
library(colorBlindness)
mat = matrix(1:81, nrow = 9, ncol = 9)

library(ggplot2)
library(reshape2)
cols = limno_palette("IowaSummer")

mat1 = melt(t(mat[9:1, ]))
len = length(cols)-1
mat1$v2 = cut(mat1$value,
              breaks = seq(0,ceiling(81/len)*len, 
                           length.out = len+1))
ht = ggplot(mat1) + 
  geom_tile(aes(x=Var1, y=Var2, fill=v2)) + 
  scale_fill_manual(values=cols) + 
  theme_bw()

# check the plot by CVD simulator
cvdPlot(ht)
```


```{r,fig.width=9,fig.height=7,echo=TRUE,include=TRUE}
# Second Example
cols = limno_palette("Bloom2",10, "continuous")

mat1 = melt(t(mat[9:1, ]))
len = length(cols)-1
mat1$v2 = cut(mat1$value,
              breaks = seq(0,ceiling(81/len)*len, 
                           length.out = len+1))
ht = ggplot(mat1) + 
  geom_tile(aes(x=Var1, y=Var2, fill=v2)) + 
  scale_fill_manual(values=cols) + 
  theme_bw()

# check the plot by CVD simulator
cvdPlot(ht)
```

***
